\section{Customer Perspectives}
\label{sec:customer_perspective}

Career counseling can be provided to a wide range of different clients. Especially, clients may be
in different stages of their career. A client may be in the process of finishing school or university
and about to enter the job market. Another client might already have several years of work experience
and looking to optimize his or her career. A third client may be in the process of re-entering the job
market after a period of absence, such as unemployment or a parental leave. Due to totally different
\textit{life} circumstances, the customer perspectives might be entirely different. Considering the
Maslow pyramid of needs \citep{maslowTheoryHumanMotivation1943}, a client in the process of re-entering
the job market might be more concerned with the basic needs (such securing access to food and shelter)
than a client who has an established career and is seeking a career optimization. The latter might be
more concerned with the higher needs of self-actualization. Although we will subsequently only develop
a persona for one customer segment, we nevertheless want to shed light on the individual needs of the
three client archetypes.

\subsection{Job Market Entry}

Students, graduates, young professionals and other job market entrants are often faced with the
challenge of finding a suitable job. As they do not have or just have a little previous work experience,
they face challenges in finding a job that matches their skills and interests. They often lack the necessary
knowledge to successfully apply for a job. Job market entrants may also lack knowledge about the employer
or its industry potentially leading to a mismatch between the entrant's expectations and the reality of the
job.

\subsection{Career Transition}

\subsection{Seeking Reintegration into the Job Market}

\subsection{Companies Engaged in the ``War for Talent''}