\section{Evaluation}
\label{sec:evaluation}

Competition


While LinkedIn is arguably the most dominant player in terms of employee data in Western countries,
there are plenty of other companies that have access to employee data. However, the databases of competitors are
not as large as LinkedIn's or are focused on a particular country or regions. While these databases are certainly
relevant in some career paths and countries, they are not as relevant in others or for international careers.

% @TODO fact check the whole paragraph - if this is all true, this can be an interesting addition!
In Germany, there is Xing, which is a German company that is also active in Switzerland and Austria.
In China, there is Maimai, which is
a Chinese company that is also active in China. In India, there is Naukri, which is an Indian company that is also
active in India. In Russia, there is HeadHunter, which is a Russian company that is also active in Russia. In Japan,
there is Wantedly, which is a Japanese company that is also active in Japan. In South Korea, there is Saramin, which
is a South Korean company that is also active in South Korea. In Brazil, there is Vagas, which is a Brazilian company
that is also active in Brazil. In Mexico, there is OCC, which is a Mexican company that is also active in Mexico.
In the United States, there is Indeed, which is an American company that is also active in the United States. In
Canada, there is Workopolis, which is a Canadian company that is also active in Canada. In Australia, there is
Seek, which is an Australian company that is also active in Australia. In New Zealand, there is Trade Me, which is
a New Zealand company that is also active in New Zealand. In South Africa, there is CareerJunction, which is a
South African company that is also active in South Africa. In Nigeria, there is Jobberman, which is a Nigerian
company that is also active in Nigeria.
